Decomposing biodiversity change to processes of extinction, colonization, and persistence across scales

### 2023-04-20 scripts/ms_scaling_changes.qmd
initial commit

This document contains the code to reprodcuce the models fitting and figures for our manuscript. Models were created for the 2 datasets we used, *i.e.* the Czech bird Atlases (hereafter CzAtlas) and the Czech breeding bird survey (hereafter CzBBS). Those datasets are provided already processed (*i.e.* species richness, colonization, extinction... per unit of area). If you are interested in accessing those datasets, feel free to contact the following email address: leroy\@fzp.czu.cz.

>>>>

This document contains the code to reproduce the models fitting, the predictions and the figures of our manuscript. We modeled **1)** species richness, **2)** numbers and **3)** probabilities of extinction, colonization and persistence. Models were fitted for the Atlas datasets (hereafter CzAtlas) on one hand and for the Czech Breeding Birds Survey on the other hand (hereafter CzBBS, or JPSP for Jednotný program sčítání ptáků) using repeated cross-validation with 3 different tree-based algorithms.

The data provided (*i.e.* CzAtlas and CzBBS) are already processed into species richness, colonization, extinction... per unit of area. If you are interested in accessing the raw datasets, feel free to contact the following email address: leroy\@fzp.czu.cz.
